Robotic Manipulator Path Planning Utilizing Interpolated 3D Voxel-Based Obstacle Avoidance Method

### 2023-11-09 Articles/Article 1/main.tex
further article structure creation
working title manipulation

%opening
\title{Robotic Manipulator Path Planning Utilizing Interpolated 3D Voxel-Based Obstacle Avoidance Method}
\author{Jakob Baumgartner, Gregor Klančar}

@@

\section{Related Works}

@@

\section{Method}

@@

\section{Experiments and simulations}

\add{
	- include execution times}

>>>>

%opening
\title{\comment{3D Voxel Grid Based Path Planning for Robotic Manipulators through Matrix Multiplication Techniques}{Alternatives:\\ - Matrix Multiplication-Driven Repulsive Fields for 3D Voxel-Based Robotic Manipulator Path Planning \\ - Robotic Manipulator Path Planning Optimization Using Matrix-Derived Repulsive Fields Based on 3D Voxel Grid}}

\author{Jakob Baumgartner, Gregor Klančar}

@@

\section{Background}

@@

\section{Methodology}

@@

\section{Results}

\add{
	- include execution times \\
	- PLOT: kernel on robot graphics \\
}

\section{Discussion}

\add{
	- add the limitations of such method \\
	- the limitations of local search \\
	- number of parameters that need to be tuned (are there actually that many?)
}

\section{Conclusion}
